draft_final_assignment

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

```{r}
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
```

@@

##Creatung a dfm from the corpus
```{r }
dfm_corp <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm()

@@

##Most common words in the corpus
```{r }
dfm_corp %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
```
#Wordcloud congress 115

```{r }
dfmat115 <- dfm(corpus_subset(corp, session == 115), remove = stopwords("english"), remove_punct = TRUE,
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat115, max_words = 300)
```

@@

```{r }
dfmat116 <- dfm(corpus_subset(corp, session == 116), remove = stopwords("english"), remove_punct = TRUE, 
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat116, max_words = 300)
```

#Wordcloud congress 117

```{r }
dfmat117 <- dfm(corpus_subset(corp, session == 117), remove = stopwords("english"), remove_punct = TRUE,
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat117, max_words = 300)
```

#Wordcloud comparing Democrats and Republicans
```{r }
#Need to get sponser party data

@@

tfreq <- dfm_corp %>%
  textstat_frequency() %>%
  head(20)

@@

```{r }
# Most common words by Congressional session 115
df_115 <- df %>%
  filter(session == "115")

dfmat_115 <- df_115$summary %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm()

tfreq_115 <- dfmat_115 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r }
# Most common words by Congressional session 116
df_116 <- df %>%
  filter(session == "116")

dfmat_116 <- df_116$summary %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm()

tfreq_116 <- dfmat_116 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r}
# Most common words by Congressional session 117
df_117 <- df %>%
  filter(session == "117")

dfmat_117 <- df_117$summary %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm()

tfreq_117 <- dfmat_117 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r}
df$era <- ifelse(df$session == 116, "Pre", "Post")

ytfreq <- dfm_corp %>% 
  textstat_frequency(groups = df$era) %>%
  pivot_wider(id_cols=feature, names_from=group, values_from=frequency)

ggplot(ytfreq, aes(x="Post", y="Pre")) + 
  geom_point() +
  coord_fixed()
```

>>>>

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
```

@@

##Creatung a dfm from the corpus
```{r }
dfmat <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm()

@@

##Most common words in the corpus
```{r }
dfmat %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
```
#Wordcloud congress 115

```{r }
dfmat_115 <- dfm(corpus_subset(corp, session == 115), remove = stopwords("english"), remove_punct = TRUE,
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat_115, max_words = 300)
```

@@

```{r }
dfmat_116 <- dfm(corpus_subset(corp, session == 116), remove = stopwords("english"), remove_punct = TRUE, 
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat_116, max_words = 300)
```
#Wordcloud congress 117

```{r }
dfmat_117 <- dfm(corpus_subset(corp, session == 117), remove = stopwords("english"), remove_punct = TRUE,
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat_117, max_words = 300)
```

#Wordcloud comparing Democrats and Republicans
```{r }
#Need to get sponsor party data

@@

tfreq <- dfmat %>%
  textstat_frequency() %>%
  head(20)

@@

```{r }
# Most common words by Congressional session 115
tfreq_115 <- dfmat_115 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r }
# Most common words by Congressional session 116
tfreq_116 <- dfmat_116 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r}
# Most common words by Congressional session 117
tfreq_117 <- dfmat_117 %>%
  textstat_frequency() %>%
  head(20)

@@

##Comparing subgroups
```{r}
df <- df %>%
  mutate(session_written = ifelse(session == 115, "session_115", 
                             ifelse(session == 116, "session_116",
                             ifelse(session == 117, "session_117", NA))))

ytfreq <- dfmat %>% 
  textstat_frequency(groups = df$session_written) %>%
  pivot_wider(id_cols=feature, names_from=group, values_from=frequency)
```

```{r}
#Comparing sessions 115 and 116

#Plot #1: differences in frequency by session
ggplot(ytfreq, aes(x= session_116, y= session_115)) + 
  geom_point() + theme_minimal()

#Plot #2: coloring changes by session
ytfreq$change_115_116 <- log(ytfreq$session_116 / ytfreq$session_115)
max_change <- max(abs(ytfreq$change_115_116), na.rm=TRUE)

ggplot(ytfreq, aes(x=session_116, y=session_115, fill=change_115_116)) + 
  geom_point(color="grey", shape=21) +
  scale_fill_gradientn(
    colors = c("#4575b4","white","#d73027"),
    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change))+
theme_bw()

#Plot 3: labeling words with biggest change
labels <- ytfreq %>% 
  rowwise() %>% 
  mutate(max_value = max(session_116, session_115)) %>% 
  filter((abs(change_115_116)>0.4 & max_value>2.5) )

ggplot(ytfreq, aes(x=session_116, y=session_115, fill=change_115_116)) + 
  geom_point(color="grey", shape=21) +
  scale_fill_gradientn(
    colors = c("#4575b4","white","#d73027"),
    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change)) + theme_bw() +
  geom_label_repel(data=labels, aes(label=feature), min.segment.length = 0)
```

```{r}
#Comparing sessions 116 and 117
ggplot(ytfreq, aes(x= session_117, y= session_116)) + 
  geom_point() + theme_minimal()

#Plot #2: coloring changes by session
ytfreq$change_116_117 <- log(ytfreq$session_117 / ytfreq$session_116)
max_change <- max(abs(ytfreq$change_116_117), na.rm=TRUE)

ggplot(ytfreq, aes(x=session_117, y=session_116, fill=change_116_117)) + 
  geom_point(color="grey", shape=21) +
  scale_fill_gradientn(
    colors = c("#4575b4","white","#d73027"),
    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change))+
theme_bw()

#Plot 3: labeling words with biggest change
labels <- ytfreq %>% 
  rowwise() %>% 
  mutate(max_value = max(session_117, session_116)) %>% 
  filter((abs(change_116_117)>0.4 & max_value>2.5) )

ggplot(ytfreq, aes(x=session_117, y=session_116, fill=change_116_117)) + 
  geom_point(color="grey", shape=21) +
  scale_fill_gradientn(
    colors = c("#4575b4","white","#d73027"),
    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change)) + theme_bw() +
  geom_label_repel(data=labels, aes(label=feature), min.segment.length = 0)
```
